Reproducibility in Plant Pathology

### 2021-07-21 README.rmd
Update README with link to docx file and update address

A script, `knit_paper.R`, is located in `analysis/paper/knit_paper.R` that will knit the Word document in a Docker session.

@@

Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(), "%Y")`, copyright holder: Adam H Sparks

@@

Adam H Sparks
Senior Research Scientist
Farming Systems Innovation
Primary Industries Development
Department of Primary Industries and Regional Development
Level 5, 1 Nash St Perth WA 6000

>>>>

A script, `knit_paper.R`, is located in `analysis/paper/knit_paper.R` that will knit the [Word document](analysis/paper/paper.docx) in a Docker session.

@@

Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(), "%Y")`, copyright holder: Adam H. Sparks

@@

Adam H Sparks
Senior Research Scientist
Farming Systems Innovation
Primary Industries Development
Department of Primary Industries and Regional Development
Level 6, 1 Nash St., Perth WA 6000
